---
title: "Data Udacity"
author: "Christoph Knoop"
date: "2 April 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```



Quality of Red Wine by Christoph Knoop
========================================================

# Abstract

What makes a good wine? Centuries of tradition, solid craftsmanship? I'm sure 
it is. But the quality of a wine also has something to do with what it contains chemically.The Question: Can we derive its quality from the chemical 
composition of a wine? 

# Source of Dataset

  P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis. 
  Modeling wine preferences by data mining from physicochemical properties.
  In Decision Support Systems, Elsevier, 47(4):547-553. ISSN: 0167-9236.

  Available at: 
  [@Elsevier] http://dx.doi.org/10.1016/j.dss.2009.05.016
  [Pre-press (pdf)] http://www3.dsi.uminho.pt/pcortez/winequality09.pdf
  [bib] http://www3.dsi.uminho.pt/pcortez/dss09.bib

# Analysis

In this document I examine the quality of red wines. For this I use a data set 
of four authors (more information at 'Source of Dataset') provided by Udacity. 
It contains data on 1599 wines. Listed are 13 variables. 11 of them are 
concerned with the chemical composition of the wines, one with the result of 
qualitative wine tests. The 13th variable is the ID of the wine. The Dataset 
includes samples of the Portugese "Vinho Verde" wine.   


```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

library(ggplot2)
library(dplyr)
library(data.table)
library(gridExtra)
library(ggthemes)
# libraries for scatter plot matrix
library(GGally)
library(corrr)
library(corrplot)
library(psych)
library(PerformanceAnalytics)
library(ggcorrplot)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
df <- read.csv("wineQualityReds.csv")

```

**A first look at the dataset**
 

```{r echo=FALSE, message=FALSE, warning=FALSE}
dim(df)
summary(df)
str(df)
```
# Explanation of the attributes

This explanation is part of the original dataset: 
**1 - fixed acidity:** most acids involved with wine or fixed or nonvolatile 
(do not evaporate readily)

**2 - volatile acidity:** the amount of acetic acid in wine, which at too high 
of levels can lead to an unpleasant, vinegar taste

**3 - citric acid:** found in small quantities, citric acid can add 'freshness'
and flavor to wines

**4 - residual sugar:** the amount of sugar remaining after fermentation stops, 
it's rare to find wines with less than 1 gram/liter and wines with greater than
45 grams/liter are considered sweet

**5 - chlorides:** the amount of salt in the wine

**6 - free sulfur dioxide:** the free form of SO2 exists in equilibrium between
molecular SO2 (as a dissolved gas) and bisulfite ion; it prevents microbial
growth and the oxidation of wine

**7 - total sulfur dioxide:** amount of free and bound forms of S02; in low
concentrations, SO2 is mostly undetectable in wine, but at free SO2
concentrations over 50 ppm, SO2 becomes evident in the nose and taste of wine

**8 - density:** the density of water is close to that of water depending on the
percent alcohol and sugar content

**9 - pH:** describes how acidic or basic a wine is on a scale from 0 
(very acidic) to 14 (very basic); most wines are between 3-4 on the pH scale

**10 - sulphates:** a wine additive which can contribute to sulfur dioxide gas 
(S02) levels, wich acts as an antimicrobial and antioxidant

**11 - alcohol:** the percent alcohol content of the wine

Output variable (based on sensory data): 
**12 - quality** (score between 0 and 10)




# Univariate Plots Section



```{r echo=FALSE, message=FALSE, warning=FALSE, quality}
ggplot(aes(quality), data=df) + geom_histogram()
df$quality.factor <- factor(df$quality)
summary(df$quality.factor)

```

As we can see, most of the wines examined are of average **quality**. On a scale
of 1 to 10, the wines of quality level 5 make up the largest sample with 681, 
followed by wines of level 6. 82.49 percent of the wines come from the two 
middle quality levels 5 and 6. The best categories 9 and 10 are not represented
at all in the data set, this also applies to the lowest levels 0 to 2. 
I introduced a variable with quality.factor. Here the quality assessments are 
arranged as  factor variables. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(fixed.acidity), data=df) + geom_histogram()
summary(df$fixed.acidity)
```
The lowest degree of **fixed acidity** is 4.6, the highest is 15.90. Especially 
in the upper values there are a few prominent outliers (14 and higher). The main
part of the wines has an acidity of 7.1 (1st quartile) and 9.20 (3rd quartile). 
The average is 8.32, the median 7.9. 

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(aes(volatile.acidity), data= df) + geom_histogram(bins=50)
summary(df$volatile.acidity)

```

The **volatile acidity** is of particular interest, as a high proportion can 
trigger a vinegar taste of the wine. The lowest acidity in the wines tested is 
0.12, the highest is 1.58. Most of the values are between 0.39(1st quartile) and
0.64 (3rd quartile). The average amounts to 0.5278, the median is 0.52. The 
higher values show some high outliers (more than 1.2). Since a high acid value 
can lead to a bad taste, the question is interesting whether the high values are
reflected in a loss of quality. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(citric.acid), data=df) + geom_histogram(bins=50)
summary(df$citric.acid)



```
**Citric acid** also has a strong influence on the taste. The higher their 
proportion, the fresher the wine can taste. The question for later analysis: 
Does a taste altered by citric acid also ensure a higher quality? 
A look at the histogram shows that many wines do not contain any citric acid at 
all, the histogram also shows two peaks at an acid content of 0.25 and 0.5. The 
highest value is a violent outlier and is at 1. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(residual.sugar), data=df) + geom_histogram(bins=50)
ggplot(aes(residual.sugar), data=df) + geom_histogram(bins=50) +
  scale_x_continuous(limits = c(0,6))
ggplot(aes(residual.sugar), data=df) + geom_histogram(bins=50) +  scale_x_log10(breaks=seq(1,16,2))
summary(df$residual.sugar)

# creating new variable with bins for sweetness
df$sweetness <- cut(df$residual.sugar, c(0,4,12, 45, max(df$residual.sugar)), labels=c("dry", "semi-dry", "medium", "sweet"))

ggplot(aes(sweetness), data=df) + geom_histogram(stat="count")

```

The degree of sweetness of the wine depends on the **residual sugar**. Here it 
makes sense to create a new variable that divides the wines into four 
categories. These categories are derived from European Union regulation. 
According to this, a wine with up to 4 mg sugar per litre is considered dry, 
between 5 and 12 mg per litre as semi-dry, between 13 and 45 grams per litre as
medium and with a sugar value of more than 45 grams per litre as sweet.We call 
that new variable "sweetness". 

Here is the source: *https://en.wikipedia.org/wiki/Sweetness_of_wine*

In order to increase the significance of our sugar histograms, the second plot 
is a zoom into the range up to a sugar content of 6 grams per litre. 
In the third diagram I scaled the X-axis with Log10() to show the distribution 
even more clearly. 

The plots show Most of the wines can be classified in the dry category, between 
1.9 (1st quartile) and 2.6 (3rd quartile). However, we have an outlier with a 
significantly higher sugar content of up to 15.5. 

Our variable "sweetness" shows that the majority of the wines examined have the
attribute "dry" according to the EU classification. 


```{r echo=FALSE, message=FALSE, warning=FALSE, chlorides}
ggplot(aes(chlorides), data=df) + geom_histogram(bins=80)
ggplot(aes(chlorides), data=df) + geom_histogram(bins=80) +  
  scale_x_continuous(lim=c(0, 0.2)) + labs(x="Zoom in - chlorides limited")
ggplot(aes(chlorides), data=df) + geom_histogram(bins=80) + 
  scale_x_log10() + labs (x="Chlorides log10")
summary(df$chlorides)
```

Most of the wines have a **sodium chloride** content between 0.07 grams per 
liter (1st quartile) and 0.09 grams per liter (3rd quartile). The median is 
0.079 grams per liter, the average is 0.08747 grams per liter. Occasionally we 
find outliers of up to 0.611 grams per litre in the wines. 

The salt content is responsible for the occurrence of tartar. Whether this has 
an effect on the evaluation of wine testers will be analysed at a later date.

```{r echo=FALSE, message=FALSE, warning=FALSE}
summary(df$free.sulfur.dioxide)
summary(df$total.sulfur.dioxide)

g1 <- ggplot(aes(free.sulfur.dioxide), data=df) + geom_histogram(bins=50)
g2 <- ggplot(aes(total.sulfur.dioxide), data=df) + geom_histogram(bins=50)
grid.arrange(g1,g2)

```
Sulphur is important for the preservation of a wine, otherwise the liquids can
oxidize very quickly. Moreover, sulphur enhances the taste, without sulphur a 
wine would taste more like a path.  Above all sweet wines have to be sulphured. 
There are discussions whether sulphurization has a negative effect on the 
quality of the wine. We can investigate this later. therefore the question: Does
low sulphur ensure more quality?  

This free sulphur is what can possibly smell and cause health problems if the 
wine has been over-sulphured. For the health evaluation it depends therefore on
the content of free sulphurous acid. Free sulphur above 50 mg/litre is clearly
noticeable. 

In relation to the total sulphur, the free sulphurous acid accounts for almost
20 percent and the bound sulphur for more than 80 percent.

In our data set, the low value for free sulfur is 1.0, the highest value is 72 
(median 14, average 15.87).

The lowest value for total sulphur is 6, the highest is 289, the median is 38, 
the average is 46.47. 

For both values we see a large gap between the 3rd quartile and the highest 
value. So we are dealing here with extreme outliers. 


```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(aes(density), data=df) + geom_histogram(bins=50)
summary(df$density)


```
The **density of the wine** indicates something for the proportion of must in 
the liquid.  The higher, the heavier the must, for example late ripened grapes 
with a high sugar content. However, the sugar content of the must is only part 
of the taste of a wine. 

As a rule of thumb, the sweeter a wine, the higher its density. 

The lowest density in our data set is 0.9901, the highest 1.0037. The median is 
0.9968, the average is 0.9968. Since the maximum value of 1.0037 is only 
slightly higher than the 3rd quantile, we obviously only have to deal with a 
few and not particularly extreme outliers. 


```{r echo=FALSE, message=FALSE, warning=FALSE, pH}
ggplot(aes(pH), data=df) + geom_histogram()
summary(df$pH)



```
The **pH value** plays an important role in the taste of wine and is connected 
to the acids contained in the wine. In our data set most of the wines examined 
show a value from 3,210 (1st quartile) to 3.4 (3rd quartile). The smallest value
is 2.74, the highest is 4.01. The median is 3.310, the average is 3.311. So the
median and average are almost congruent, meaning: there are hardly any outliers. 

```{r echo=FALSE, message=FALSE, warning=FALSE, sulphates1}
ggplot(aes(sulphates), data= df) + geom_histogram(bins=50)
ggplot(aes(sulphates), data=df) + geom_histogram(binwidth=0.03) + scale_x_continuous(lim=c(0.2,1), breaks=seq(0.2,1, 0.2))
ggplot(aes(sulphates), data=df) + geom_histogram(binwidth=0.03) + scale_x_log10(breaks=seq(0, 1.5, 0.2)) + labs(x="sulphates scale_x_log10")
summary(df$sulphates)

```
The variable **sulphates** describes the potassium content of the wine. 
Potassium is part of the acidity of the wine. Too little potassium has a 
negative effect on the taste. Too much potassium, on the other hand, can lead 
to a too high pH value and thus to a soapy taste.

The smallest value is 0.33, the highest is 2, the median is 0.62, the average 
0.6581, the 3rd quantile 0.73. This means that the maximum value of 2 is a 
severe outlier. 

```{r echo=FALSE, message=FALSE, warning=FALSE, alcohol}
ggplot(aes(alcohol), data=df) + geom_histogram(bins=50)


```
The **alcohol** value in wine is not necessarily a quality feature. However, 
alcohol has an influence on the taste. A higher alcohol content usually provides
a fuller, more intense aroma. The fermentation of wines with a low alcohol 
content was usually stopped early, so that more residual sugar often remains in
the wine. Say: The wine is usually sweeter. Often wine has an alcohol value 
between 9 and 11 percent. 
In our data set, the average alcohol content is 10.42 percent. The median is 
10.20 percent. The lowest value is 8.4 percent, the highest 14.9 percent. 







# Univariate Analysis

In the dataset we find many variables whose values can influence the quality of
a wine. However, even experts have different points of view as to which values
and at what level make up a good wine. The bottom line is that it is a 
combination of the different ingredients that make a wine stand out. 

The task of the following analysis will be to identify links between the 
individual characteristics of the wine and to try to reconcile specific 
information on ingredients with the established quality of the wine. 

The quality variable is indispensable for this, it´s our main feature. The 
quality of a wine cannot be measured objectively on the basis of figures. 
However, the various test results with which wine experts have evaluated our 
data set allow us to draw conclusions and establish connections. 



# Bivariate Plots Section


```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots}
set.seed(1836)
df_sample <- df[sample.int(nrow(df), 1000), ][, c(2:13)]
ggcorr(df_sample, nbreaks=8, palette='RdGy', label=TRUE, label_size=5, 
       label_color='white')
df_small <- df_sample[ ,c(2:3, 10:12)]
ggpairs(df_small, 
        lower=list(continuous = wrap("points", shape= I("."))),
        upper = list(combo=wrap("box", outlier.shape = I("."))))



```

At the beginning, we use ggcorr to provide a rough overview of the correlations 
between the individual variables. We are particularly interested in what the 
quality of the wines. 

After a look at our overview it becomes clear that the quality shows with others
values have hardly any stronger correlations. Only for the alcohol content 
(corr 0.5) and for the proportion 
The volatile acidity (correlation of 0.4) shows stronger correlations. Compound
s still exist between quality and sulphur as well as quality and citric acid 
(each 0.3).  
We assume that with values of +/- 0.3 significant 
correlations exist, with values between 0.4 and 0.6 of strong 
correlations can be spoken and values above +/- 0.7 are very high.
strong correlations. The latter, however, come in our record 
not before. 

With ggpairs we then look at some values with strong correlation still
a little more precisely. These pairs of variables are now to be examined in more
detail. 


```{r echo=FALSE, warning=FALSE, message=FALSE, alcohol_quality}

ggplot(aes(x=quality, y=alcohol), data=df) + 
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0))

ggplot(aes(x=factor(quality), y=alcohol), data=df) + 
  geom_boxplot()

df_sum = df_sample %>% group_by(quality) %>% summarize(alc_mean = mean(alcohol), alc_median=median(alcohol), n=n())

ggplot(aes(x=quality, y=alcohol), data=df) + 
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0)) + 
  geom_line(stat="summary", fun.y = mean, linetype=2, color="blue")

ggplot(aes(x=quality, y=alcohol), data=df) + geom_bar(stat="summary", 
  fun.y = mean,linetype=2, color="blue") + coord_cartesian(ylim=c(9, 12.2)) +
  scale_x_continuous(breaks=seq(3,8,1))


```

The wines of the highest quality have a high **alcohol** content on average. The
higher the quality of the wine, the higher the average alcohol content. The 
exception is quality level 5, in which there are many wines with an alcohol 
content of less than 10 percent. The average alcohol content of this quality 
class is therefore slightly lower than that of grades 4 and 5, but the average 
alcohol content rises sharply for higher quality classes.

```{r echo=FALSE, message=FALSE, warning=FALSE, volatil_acidity}
ggplot(aes(x=quality, y=volatile.acidity), data=df) + 
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0))

ggplot(aes(x=factor(quality), y=volatile.acidity), data=df) + 
  geom_boxplot()


ggplot(aes(x=quality, y=volatile.acidity), data=df) + 
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0)) + 
  geom_line(stat="summary", fun.y = mean, linetype=2, color="blue")


```

In principle, the wines of higher quality show less **volatile acidity** than 
the wines of the lower quality classes. This was to be expected, because acidity
can give the wine a vinegar taste. The fact that some wines with a high 
proportion nevertheless slip into the higher quality classes could indicate that
some testers certainly appreciate the high proportion of volatile acidity as a 
special note of the wine. 






```{r echo=FALSE, message=FALSE, warning=FALSE, sulphates}
ggplot(aes(quality, sulphates), data=df) + 
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0)) + 
  geom_line(stat="summary", fun.y = mean, linetype=2, color="blue")
ggplot(aes(quality, sulphates), data=df) + 
  geom_bar(stat="summary", fun.y = mean)
ggplot(aes(quality, sulphates), data=df) + 
  geom_bar(stat="summary", fun.y = median)
ggplot(aes(x = factor(quality), sulphates), data=df) + 
  geom_boxplot()


```
High quality wines also have an average higher value of sulphates in our data 
set. This can be determined with both the average and the median. This is 
important because there are many outliers, especially in quality levels 5 and 6,
and the median tends to be less sensitive. It should also be noted that in the 
two highest measured quality levels (7 and 8) there are no sulphate values above
1.7, but at the lower values the Outlets go up to the value 2. 



```{r echo=FALSE, message=FALSE, warning=FALSE, citric.acid}
ggplot(aes(x=factor(quality), y=citric.acid), data=df) + geom_boxplot()

ggplot(aes(x=quality, y=citric.acid), data=df) + 
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0)) + 
  geom_line(stat="summary", fun.y = mean, linetype=2, color="blue")

```
Quality and citric acid are also related. On average, the higher quality wines 
contain more citric acid. However, the range of values is very wide, especially 
in the lower quality classes. And: Even high class wines (quality 8) contain 
very little citric acid in individual cases. 



```{r echo=FALSE, message=FALSE, warning=FALSE, sugar, fig.width=6.9,fig.height=4}
ggplot(aes(x=quality, y=residual.sugar), data=df) +
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0)) +
  geom_line(stat="summary", fun.y = mean, linetype=2, color="blue")
ggplot(aes(x=factor(quality), y=residual.sugar), data=df) +
  geom_boxplot()

```

A final quick test that confirms our observations from the correlation overview.
In our data set, the sweetness of the wine has no clear influence on the quality
of the wine. The average values are almost the same in the different quality 
levels. 
However, it is remarkable that the particularly sweet wines (from a sugar 
content of 12) can only be found as outliers in the middle quality classes.  

```{r echo=FALSE, message=FALSE, warning=FALSE, alcohol/density}
ggplot(aes(x=alcohol, y=density), data=df) + 
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0)) + 
  geom_line(stat="summary", fun.y = mean, linetype=1, color="red") + 
  geom_smooth(span=0.3)

```
There is a correlation between density and alcohol content. As the graph shows, 
wines with a higher alcohol content have a lower average density. 

```{r echo=FALSE, message=FALSE, warning=FALSE, fixed.acidity/density}

ggplot(aes(x=fixed.acidity, y=density), data=df) +
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0)) +
  geom_line(stat="summary", fun.y = mean, linetype=1, color="red") +
  geom_smooth(span=0.3)

ggplot(aes(x=density, y=fixed.acidity), data=df) +
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0)) +
  geom_smooth(span=0.3)

```
In our data set there is a relationship between the density of the wines and the
fixed acidity. The higher the density of the wine, the higher the fixed acidity. 

```{r echo=FALSE, message=FALSE, warning=FALSE, fixed.acidity/alc}

ggplot(aes(x=fixed.acidity, y=alcohol), data=df) +
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0)) +
  geom_line(stat="summary", fun.y = mean, linetype=1, color="red") +
  geom_smooth(span=0.3)

ggplot(aes(x=alcohol, y=fixed.acidity), data=df) +
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0)) +
  geom_smooth(span=0.3)

```
The alcohol content has an effect on the quality of the wine, as does the 
volatile acidity. However, a test to determine whether these two variables are 
also related is negative. Only wines with the highest measured alcohol values 
tend to have a lower acid content. However, the values measured there are not 
very numerous. 

```{r echo=FALSE, message=FALSE, warning=FALSE, fixed.acidity/alcohol}
ggplot(aes(x=density, y=fixed.acidity), data=df) +
  geom_hex() +
  scale_fill_gradient(high="red", low="blue")

ggplot(aes(x=density, y=fixed.acidity), data=df) +
  geom_bin2d(binwidth=c(0.0005,0.3)) +
  scale_fill_gradient(high="red", low="blue")

ggplot(aes(x=density, y=fixed.acidity), data=df) +
  geom_point(alpha=0.4, shape=19, position=position_jitter(h=0)) +
  geom_smooth(span=0.3)




```
Finally, we look at the values of our variable pair with the strongest 
correlation - density and fixed acidity. The higher the density of the wine, the
higher the fixed acidity. 



# Bivariate Analysis

The question of this analysis is simple to summarize: What is the quality of a 
good wine? In addition to the quality, four of our variables seem to be of 
particular importance. 
The alcohol content of good wines is on average higher. Furthermore, good wines 
have a lower volatile acidity content. The sulphur content is also higher for 
wines of higher quality than for wines of lower quality. However, it should be 
noted that the rule "more sulphur, higher quality" does not work. None of the 
particularly high-quality wines has a sulphur value above 1.2. In contrast, the
wines of lower quality have values of 1.5 as outliers. 
The amount of citric acid also seems to have an influence on the quality of the 
wine. For example, the high-class wines have on average a higher proportion of 
citric acid. However, even this variable does not seem to be suitable for 
significantly determining the quality of the wine.  This means that even wines 
of a high quality level have values close to zero. 

It should be noted that values that more or less correlate with the quality of 
the wine are not linked to each other. It could be assumed that - if a high 
alcohol value is more indicative of the quality of a wine - wines with a low 
proportion of volatile acidity also have a high alcohol content. However, this 
connection is not given in our data set. 

We measured the highest correlation between the density and the proportion of 
fixed acidity. This allows the conclusion that during the fermentation process a
wine with a high must content forms the measured acids faster than with a low 
must content. 


# Multivariate Plots Section



```{r echo=FALSE, warning=FALSE, message=FALSE, sulphates_alcohol}

df$quality_bins <- cut(df$quality, c(1,4,6,10), 
                       labels=c("lowest quality", "medium quality", 
                                "high quality"))
ggplot(aes(x=sulphates, y=alcohol), data=df) +
  geom_point(aes(color=factor(quality_bins)))

```
To make the analysis more meaningful, we first arrange the wines according to 
quality in three bins: low quality (1-4), medium quality (5-6) and high quality 
(7-10). 
When we combine the values for alcohol, sulphates and quality, we see that the 
wines with high quality increasingly have both a high alcohol and a high sulphur
value.

```{r echo=FALSE, warning=FALSE, message=FALSE, alcohol/volatileacidity}
ggplot(aes(x=alcohol, y=volatile.acidity), data=df) +
  geom_point(aes(color=quality_bins), size=4, alpha=0.2)

```

When combining volatile acidity, alcohol content and quality of wines, we find 
that wines of higher quality often have a higher alcohol content and a low 
content of volatile acidity.    



```{r echo=FALSE, warning=FALSE, message=FALSE, citric_alcohol_sulphates}
ggplot(aes(x=citric.acid, y=sulphates), data=df) +
  geom_point(aes(color=quality_bins, size=alcohol), alpha=0.3) +
  scale_radius(range=c(0.5,10), breaks = c(10, 11, 12, 13, 14)) +
  coord_cartesian(ylim = c(0.3, 1.3))

```
As we can see, good quality wines often contain a higher proportion of citric 
acid and at the same time a higher proportion of sulphur. The question of
whether the alcohol content also plays a decisive role here must be answered in 
the negative with regard to our graph. Wines with high and low alcohol content 
do not show a clear pattern here. 
For more expressiveness, I cut the Y-axis and concentrated on the area in which
most of the values lie. 

```{r echo=FALSE, warning=FALSE, message=FALSE, citric_alc_sulphates}
ggplot(data=df, aes(x=citric.acid, y=volatile.acidity, fill=quality)) + 
  geom_tile(width=0.03, height=0.1, alpha=0.2) + 
  scale_fill_gradientn(colours= colorRampPalette(c("blue", "red"))(100))

```
On the basis of this graph we can observe the interaction between the 
exploitation of volatile acidity, citric acidity and the quality level of the 
wine. Most of the good wines have a high level of citric acidity and a low level
of volatile acidity. 


```{r echo=FALSE, warning=FALSE, message=FALSE, density_alc}

ggplot(aes(x=alcohol, y=density), data=df) + 
  geom_point(aes(color=quality_bins), alpha=0.3, size=3) 

```
Since the alcohol content correlates with both density and quality, we want to 
examine in this graph whether all three variables have patterns in common. A 
connection, however, is hardly evident here. The wines of high quality always 
have a higher alcohol content. In contrast to wines of medium quality, however,
this does not seem to make much of a difference in density.

```{r echo=FALSE, message=FALSE, warning=FALSE}
p1 <- ggplot(aes(x=alcohol, y=density), data=df) + 
  geom_point(aes(color=alcohol)) + 
  facet_grid(. ~ quality_bins) + 
  geom_smooth(method="lm", color="red")
p2 <- ggplot(aes(x=pH, y=citric.acid), data=df) +
  geom_point(aes(color=alcohol)) +
  facet_grid(. ~ quality_bins) +
  geom_smooth(method="lm", color="red")
p3 <- ggplot(aes(x=density, y=fixed.acidity), data=df) +
  geom_point(aes(color=alcohol)) +
  facet_grid(. ~ quality_bins) +
  geom_smooth(method="lm", color="red")
grid.arrange (p1,p2,p3)

```
Finally, we examine whether the variables, which showed strong correlations 
among each other in the entire data set, behave similarly for all wine quality 
levels. This is the case, there are no serious differences between the 
individual quality levels. 


# Multivariate Analysis

If we connect the variables, which also individually show a correlation with the
quality, we can determine clear connections. What is surprising, however, is 
how many variables do not seem to have a direct effect on the quality of the 
wine, for example its density. This picture does not change even if we examine 
the wines individually according to their quality classes. 

------

# Final Plots and Summary


### Plot One
```{r echo=FALSE, Plot_One}

ggplot(aes(x=citric.acid, y=sulphates), data=df) +
  geom_point(aes(color=quality_bins, size=alcohol), alpha=0.3) +
  scale_radius(range=c(0.5,10), breaks = c(10, 11, 12, 13, 14)) +
  labs(color="Colors of the quality levels",size="Size alcohol content (%)")  +
  ggtitle("Relationship between sulphates and citric acid") + 
  ylab("Proportion of sulphates (grams per litre)") + 
  xlab("Proportion of citric acid (grams per litre)") + 
  coord_cartesian(xlim=c(0, 1.2), ylim=c(0.3, 1.2)) +
  theme_economist() +
  theme(legend.text = element_text(size=rel(1)), legend.justification=c(1,1),
        legend.position=c(1,1), legend.background = 
          element_rect(colour = 'black', linetype='solid'))


```

### Description One
This plot describes the ratio between sulphate and citric acid, taking into 
account the alcohol content and quality of the wine. This allows four different
variables to be related to each other. 

Clearly recognizable: The wines of the top class show rather a higher value with
the sulphates, at the same time they also contain more citric acid. The wines of
low quality fall behind in both categories. The alcohol content is of secondary 
importance.  

To make the plot as attractive as possible, I cut off the Y and X axes and 
concentrate on the area where most of the values are located. The theme used is 
the economist theme (ggthemes). 

### Plot Two
```{r echo=FALSE, warning=FALSE, message=FALSE, Plot_Two}
ggplot(data=df, aes(x=citric.acid, y=volatile.acidity, fill=quality)) +
  geom_tile(width=0.03, height=0.1, alpha=0.2) + 
  scale_fill_gradientn(colours= colorRampPalette(c("blue", "red"))(100)) +
  coord_cartesian(xlim=c(0, 0.8), ylim=c(0.1, 1.2)) +
  labs(fill="Colors\nof the\nquality levels") +
  ylab("Proportion of volatile acidity (grams per litre)") +
  xlab("Proportion of citric acid (grams per litre)") +
  ggtitle("Relationship of volatile acidity and citric acid") +
  theme_solarized() +
  scale_colour_solarized("blue") +
  geom_smooth()
```

### Description Two
The second plot shows the relationship between volatile acidity and citric 
acidity and their effect on the quality of the wines. It should be noted that 
Wines of higher quality have a rather low proportion of volatile acidity and are
for the most part below the average content of the wines in our data set. On the
other hand, they have a higher citric acid content than rather poorer wines. 

Also in this plot the X- and Y-axis were cut off, the plot concentrates on the 
part with especially many values. The solarize layout of the ggthemes library 
was used for this graphic. 

### Plot Three

```{r echo=FALSE, warning=FALSE, message=FALSE, sulphates_alcohol1}
ggplot(aes(x=sulphates, y=alcohol), data=df) + 
  geom_point(aes(color=factor(quality_bins)), size=2) +
  coord_cartesian(xlim = c(0.4, 1.2), ylim=c(9, 14)) +
  xlab("Proportion of sulphates (grams per litre)") +
  ylab("Proportion of alcohol (in percent)") + 
  labs(color="Colors of the\nwine quality levels") + 
  ggtitle("Realtionship of sulphates and alcohol") +
  theme_hc(bgcolor = "darkunica") +
  scale_fill_hc("darkunica")
  

```


### Description Three
The third plot shows that the wines of high quality have on average higher 
alcohol values and at the same time higher proportions of sulphates.
------

# Reflection
It is difficult to find clear patterns in the chemical composition when 
evaluating wines. For example, there are individual variables that correlate 
with quality, such as alcohol content or volatile acidity. The sulphates and 
citric acid content also show a weaker correlation with quality. However, these
variables do not correlate with each other. In other words: a wine with a lot of
alcohol (which indicates a high quality) does not necessarily have a 
particularly low content of volatile acidity, at least not to the extent that 
the alcohol correlates with the quality. 

This means that it may be difficult to put together the perfect "chemical 
recipe" for a good wine, even if there are some basic rules such as a low 
content of volatile acidity. Many different factors seem to have flowed into the
assessments of the testers. To a certain extent, taste is simply a question of 
taste - and not of chemistry. 

